Code for Graphs for ASN presentation

### 2020-12-27 ASNCode.Rmd
fixed leaf area graphs

```{r}
ggplot(aes(x = num.w.total, y = perc.w.ecl, color = food), data = data) + 
  theme_bw() + 
  ylim(0, 1.05) + 
  geom_point(aes(shape = treatment)) + 
  scale_shape_manual(values = c(19, 1, 17, 2)) +
  labs(x = "Number emerged", y = "Percentage of wasps eclosed", color = "Hostplant Consumed", 
       shape = "Heat Shock Status")
```

@@

>>>>

@@

```{r}
ggplot(aes(x = area, y = mass.max, color = food, shape = treatment), 
       data = data[data$para == "no", ]) + 
  theme_bw() + 
  xlim(0, 6000) + 
  ylim(0, 20) + 
  geom_point() + 
  scale_shape_manual(values = c(19, 1, 17, 2)) + 
  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (mg)",
       shape = "Treatment", color = "Hostplant Consumed")

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN4.png", width = 8, height = 5)
```

```{r}
ggplot(aes(x = area, y = mass.max, color = food, shape = treatment), 
       data = data[data$treatment != "P HS", ]) + 
  theme_bw() + 
  xlim(0, 6000) + 
  ylim(0, 20) + 
  geom_point() + 
  scale_shape_manual(values = c(19, 1, 2)) + 
  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (mg)",
       shape = "Treatment", color = "Hostplant Consumed")

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN5.png", width = 8, height = 5)
```

```{r}
ggplot(aes(x = area, y = mass.max, color = food, shape = treatment), data = data) + 
  theme_bw() + 
  xlim(0, 6000) + 
  ylim(0, 20) + 
  geom_point() + 
  scale_shape_manual(values = c(19, 1, 17, 2)) + 
  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (mg)",
       shape = "Treatment", color = "Hostplant Consumed")

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN6.png", width = 8, height = 5)
```

```{r}
ggplot(aes(x = num.w.total, y = perc.w.ecl, color = food), data = data) + 
  theme_bw() + 
  ylim(0, 1.05) + 
  geom_point(aes(shape = treatment)) + 
  scale_shape_manual(values = c(19, 1, 17, 2)) +
  labs(x = "Number emerged", y = "Percentage of wasps eclosed", color = "Hostplant Consumed", 
       shape = "Heat Shock Status")
